Development of a Python Package for Matching Observational Data

### 2022-05-06 paper/main.tex
more small edits

\paragraph{Almost Exact Matching.} Some of the most modern methods are DAME~\parencite{liu_interpretable_2019} and FLAME \cite{wang_flame_2021}, which incorporate machine-learning generated weight vectors indicating the relative importance of features to extend exact matching into the field of \emph{almost exact matching}. Each of these algorithms incorporates machine learning to compute a weight vector $\vec{w}$, indicating the relative importance of exact-matching on each feature. The algorithms each search for full exact matches first; when this is no longer possible, the weight vector is used to determine a subset of the features to search for exact matches on.
The key difference is that DAME choses a subset the features to match on by minimizing predictive error, whereas FLAME maximizes a match quality statistic that the researcher can tune via a hyperparameter; this statistic is a function of predictive error and a \emph{balance factor}, which represents the relative size of the strata of observations matched on this subset of features~\parencite{gupta_dame-flame_2021}.

>>>>

\paragraph{Almost Exact Matching.} Some of the most modern methods are DAME~\parencite{liu_interpretable_2019} and FLAME~\parencite{wang_flame_2021}. Each of these algorithms incorporates machine learning to compute a weight vector $\vec{w}$, indicating the relative importance of exact-matching on each feature. The algorithms each search for full exact matches first; when this is no longer possible, the weight vector is used to determine a subset of the features to search for exact matches on.
The key difference is that DAME choses a subset the features to match on by minimizing predictive error, whereas FLAME maximizes a match quality statistic that the researcher can tune via a hyperparameter; this statistic is a function of predictive error and a \emph{balance factor}, which represents the relative size of the strata of observations matched on this subset of features~\parencite{gupta_dame-flame_2021}.
